robustnessDraft

### 2025-09-11 draftFiguresPaper.Rmd
cleanup & robustness only social science journals

ppapersIncome <- cum %>%
  ggplot(aes(x = Year, y = n_cumulative, col = Income.group)) +
    geom_line(linewidth = 1) +
    labs(
      x = "Year",
      y = "Cumulative # of Papers",
      title = "Growth of Papers by income group"
    ) +
    theme_minimal()

@@

# 4) plot: one facet per category, colored by income group
ppapersIncomeYear <- ggplot(yearly_cat,
       aes(x = Year, y = n_cum, color = category)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ Income.group, scales = "free_y") +
  theme_minimal()

>>>>

ppapersIncome <- subset(cum, !is.na(Income.group)) %>% 
  ggplot(aes(x = Year, y = n_cumulative, col = Income.group)) +
    geom_line(linewidth = 1) +
    labs(
      x = "Year",
      y = "Cumulative # of Papers",
      title = "Growth of Papers by income group"
    ) +
    theme_minimal()

@@

# 4) plot: one facet per category, colored by income group
ppapersIncomeYear <- ggplot(subset(yearly_cat, !is.na(Income.group)),
       aes(x = Year, y = n_cum, color = category)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ Income.group, scales = "free_y") +
  theme_minimal()

### 2025-09-11 robustnessDraft.Rmd
adding unknownCountries
cleanup & robustness only social science journals

litReviewSub <- read.csv("dataNew/combined_lit-socialscience.csv")
litReview <- read.csv("dataNew/combined_lit.csv")

@@

library(stringi)
library(fuzzyjoin)

@@

```{r wasting time matching something that should not be compliated}

datasetClassification <- read.csv("output/dataClassifToPlot.csv")

test <- read.csv("dataNew/allgpt-lit_w_countries.csv") %>% 
  select(X , Title) %>% 
  rename(ID = X)

datasetClassificationMerged <- merge(datasetClassification, test, by = "ID")

write.csv(datasetClassificationMerged, "output/dataClassifToPlotTemporaryRobust.csv", row.names = F)

@@

########### ALL BELOW TO DELETE AND ADAPT WHEN CLEAN CODE..... #########
datasetClassification <- read.csv("output/dataClassifToPlotTemporaryRobust.csv")

library(stringi)
library(fuzzyjoin)

datasetClassificationR <- datasetClassification %>%
  mutate(title_clean = clean_title(Title))

robustnessSubset <- read.csv("output/robustnessSocialScience.csv")

robustnessSubset <- robustnessSubset %>%
  filter(!is.na(Title)) %>% 
  mutate(title_clean = clean_title(Title)) %>% 
  select(title_clean)

datasetClassificationR2 <- stringdist_left_join(
  datasetClassificationR, robustnessSubset,
  by = "title_clean",
  method = "lv",        # Levenshtein
  max_dist = 15,         # tweak this
  distance_col = "dist" # keep the distance
) %>%
  filter(!is.na(title_clean.y)) %>% 
  arrange(-dist) %>%          # largest distances first
  group_by(ID) %>% 
  summarize(ID = first(ID),
            Title = first(Title))

datasetClassificationRobustIDs <- unique(datasetClassificationR2$ID)

###### ALL ABOVE TO DELETE WHEN CLEAN CODE.... ######
datasetClassification <- read.csv("output/dataClassifToPlot.csv")
datasetCountries <- read.csv("dataNew/allgpt-lit_w_countries.csv")

datasetClassificationR <- subset(datasetClassification, ID %in% datasetClassificationRobustIDs)

datasetClassificationCountries <- merge(datasetClassificationR, datasetCountries %>% 
                                          select(X, Year, country) %>% 
                                          rename(ID = X),
                                        by = "ID") %>% 
  select(-reader)

@@

@@

```{r linking nb of papers with pollution levels over space and time?}

>>>>

library(tidyverse)
library(stringi)
library(fuzzyjoin)

### !!!!! ihi something weird about papers that have a translation

litReviewSub <- read.csv("dataNew/combined_lit-socialscience.csv")

@@

@@

# ```{r wasting time matching something that should not be compliated}
# 
# datasetClassification <- read.csv("output/dataClassifToPlot.csv")
# 
# test <- read.csv("dataNew/allgpt-lit_w_countries.csv") %>% 
#   select(X , Title) %>% 
#   rename(ID = X)
# 
# datasetClassificationMerged <- merge(datasetClassification, test, by = "ID")
# 
# write.csv(datasetClassificationMerged, "output/dataClassifToPlotTemporaryRobust.csv", row.names = F)
# 
# ```

@@

dataToSubset <- read.csv("output/robustnessSocialScience.csv")

datasetClassification <- read.csv("output/dataClassifToPloto4mini.csv")

datasetCountries <- read.csv("output/fullClassifCountryo4mini.csv")

datasetCountries <- datasetCountries %>% 
  select(ID, countryPartialF) %>% 
  rename(country = countryPartialF)

datasetClassificationCountries <- merge(datasetClassification, datasetCountries,
                                        by = "ID") %>% 
  select(-reader)

@@

# here is the step where we only keep papers in social science journals
datasetClassificationCountries <- subset(datasetClassificationCountries, ID %in% unique(dataToSubset$ID))

@@
